
---
title: "Untitled"
author: "Tate Green"
date: "4/8/2019"
output: html_document
---
```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(sf)
library(fs)
library(ggthemes)
library(gt)
library(tidyverse)
library(gganimate)
library(gapminder)
library(lubridate)
```

```{r, echo=FALSE, message=FALSE, warning= FALSE}

Columbus <- read_rds(url("https://stacks.stanford.edu/file/druid:tr137st9964/tr137st9964_oh_columbus_2019_02_25.rds"))
## Got the url for the Santa Ana data from the Standford Open Policing ## site and loaded it in using read_rds

download.file(url = "https://stacks.stanford.edu/file/druid:tr137st9964/tr137st9964_oh_columbus_shapefiles_2019_02_25.tgz", destfile = "shapes2.tgz", 
              quiet = TRUE)
## using download.file  i inserted the url for the shapesfile data and ## then loaded it into my system

untar("shapes2.tgz")
## we use the untar function to get the shapes data and unzip the shapes ## data file
shapes_data2 <- read_sf("oh_columbus_shapefiles/shapes.shp")
## We using read_sf to read the shapes data into what I called 
## shapes_data2
file_delete(c("shapes2.tgz", "oh_columbus_shapefiles"))
## delete files to make everything run smoother
```


```{r, echo=FALSE, message=FALSE, warning= FALSE}
arrests_oh <- Columbus %>% 
  filter(arrest_made) %>%
  filter(reason_for_stop == "Equipment Violation") %>%
  filter(!is.na(lat)) %>%
  filter(!is.na(lng)) %>%
  mutate(time = hour(time))
## first we use the columbus data and filter for arrests made and then ##filter out to only look at equipment violations as the reason for the ##stop within the arrest.  Then to filter out the data that is not ##available we can use filter again and the ! is.na() function for ##latitude and longitude.  To make the graph animated we may also use ##the mutate function after this in order to have the graph move by the ##hour.  
citation_locations <- st_as_sf(arrests_oh, 
                             coords = c("lng", "lat"), 
                             crs = 4326) 
## to plot the shapes data we first use the st_as_sf function to plot ##the data points we are looking for and then read that into geom_sf()
ggplot(data = shapes_data2) +
  geom_sf() +
  geom_sf(data = citation_locations)+
  theme_map() +
  labs(title = "Equipment Violation Arrests by Hour",
       subtitle = "Columbus, OH",
       caption = "Source: Stanford Open Policing Project")+
  theme(legend.position = c(2.0, 0.5)) +
  transition_manual(time)
## to plot the shapes data we first use the st_as_sf function to plot ##the data points we are looking for and then read that into geom_sf()
##function but first we use ggplot and put in the data as shapes_data2 ##and finally add labs to create a better more understandable graph with ##title subtitle and a source as well as the transition_manual with time ##to animate the graph to move by the hour.  The final product is a ##moving graph of Columbus, Ohio that shows the equipment violation ##arrests by the hour on a map.
